---
title: "HW1"
author: "Reed Sawyers"
date: "February 6, 2015"
output: pdf_document
---
Hey, if you are grading this I had a conference for a student organization I was involved in and wasn't able to make the first day of class, and am thus not 100% sure of the format you want us to use. I appologise if the formating is off, but hopefully my code/answers are in decent enough shape for you to interpret. 

1. 
```{r}
x <- 1
```
1A.
```{r}
101:105
seq(2,10, by = 2)
```
1B. 
```{r}
x <<- c(13,5,17,9,10)
x>9
```
X>9 prints T F T F T, meaning that it prints a logical value for each entry in x indicating whether or not the statement x>9 is true for that entry.  
  
  1C.
```{r}
x[x>9]
```
x[x>9] selects out the elements of the vector that are greater than 9 resulting in 13, 17, 10.
  
  1D.
```{r}
x == 5
```
x == 5 creates another series of logical values this time indicating if an entry is = to 5, which produces F T F F F in this case.  
  
  1E.
```{r}
x[4]
x[4:5]
```
x[4] gives you the fourth entry in the vector x which in this case is 9
x[4:5] gives you the fourth and fifth entries in x which in this case are 9 and 10.  
  
  1F. 
```{r}
mean(x)
#x(4)
```
You get the error 'Error: could not find function "x".' Basically R is trying to do a function on what is between the (). Mean is a function and X is something you can take the mean of so it works fine. On the other hand x(4) does not work, because while 4 is something you can apply a function to x is not currently defined as a function.  
  
  1G. 
```{r}
x[4] = NA
x
mean(x)
mean(x, na.rm = TRUE)
```
It might be a good idea for x to return NA for mean of a vector containing NA so the person running the code knows there is an NA in the data. If for example I was hired to investigate number of deaths in various hospitals and my data set had complete data for only 3 hospitals and NAs for 97 others I would want to know that my mean was really only representative of three hospitals which would then promt me to look back at my data and see what I got those NA's from. 
  
  2A. 
seq(5;8) to give [1] 5 6 7 8
```{r}
seq(5,8)
```

I don't even know what a ; does in R, but you should use a : when you are trying to do lists and the like.
  
  2B.
Cos 1.5 to calculate the cosine of 1.5 radians.
```{r}
cos(1.5)
```
The mistake was not including (). R doesn't know you are trying to get the cos of 1.5 without the ().  
  
  2C. 
>3+5=x to make x take the value 3+5.
```{r}
x <- (3+5)
```
You should use <- when assigning as = can confuse R. You can also use () to make things a little more clear.  
  
  2D. 
>sqrt[4*98] to find the square root of 392.
```{r}
sqrt(4*98)
```
[] is generally used when seperating out parts of data frames and vectors and the like, if you want to call a function use ().  
  
  2E. 
>10,000+ 4,000 adding two numbers to get 14,000.
```{r}
10000 + 4000
```
R doesn't do commas in numbers, they just scrw it up.  
  
  2F.
>sqrt(c(4,16,25,36))=4 intended to give [1] FALSE TRUE FALSE FALSE.
```{r}
sqrt(c(4,16,25,36)) == 4
```
 == is what you want to use when you are looking to see if one side of an equation is equal to another.  
   
  2G.
>fruit=c(apple,berry,cherry)to create a collection of names[1] "apple" "berry" "cherry".
```{r}
fruit=c("apple","berry","cherry")
fruit
```
You need to put "" around your characters to let R know thats what you want. Additionally R won't actully print your list, you then have to type >fruit.  
  
  2H. 
>x=4(3+2) where x is intended to be assigned the value 20.
```{r}
x <- 4*(3+2)
```
You should use <- and you need to put in a * or R will try to find the function 4 which doesn't exist.  
  
  2I. 
>x/4=3+2 where x is intended to be assigned the value 20.
```{r}
x <- (3+2)*4
```
Use a multiplication symbol to indicate that is what you want, put () around things, and simplyify expressions.
  
  3. 
```{r}
bodyfat=read.delim("http://sites.williams.edu/rdeveaux/files/2014/09/bodyfat.txt")
```
  
  3A.
```{r}
summary(bodyfat)
```
Summary gives the Min, 1st Quartile, Median, Mean, 3rd Quartile and Max for each variable in the data frame.  
  
  3B. 
```{r}
plot(bodyfat)
```
When I do plot(bodyfat) I get a bunch of scater plots. I think I have one for every variable plotted against every other variable, which is extremely overwhelming. It might be better if I was able to extract individual plots.  
  
  3C.
```{r}
names(bodyfat)
```

  3C I. 
```{r}
mean(bodyfat$Weight)
mean(bodyfat$Neck)
```

  3C II. 
```{r}
with(bodyfat,mean(Weight))
with(bodyfat,mean(Hip))
```
  
  3C III. 
```{r, warning=FALSE, message=FALSE}
plot(Weight~Height,data=bodyfat)
library(mosaic)
plot(Weight~Height,data=bodyfat)
favstats(Height, data=bodyfat)
```
Um I'm not sure how you want us to show I completed swirl lessons, I can give you some screenshots of completed lessons if you want?


  4.  
    
  4A. The population of interest is presumubly men in sweden.
    
  4B. This is a sample, they are not gathering data on all men in sweden.
  
  5.  
    
  5A. The population of interest is defective cylenders used in agricultural front end loaders and accessories produced by the engineer's company.  
    
  5B. This is a sample, he does not have all the defective cylenders. 
    
  
  6. These are convenience samples because my hotels internet is terrible and won't even load the websites.  
    
  6A. Sample of 5 companies on the NYSE
*Apple
*Microsoft
*Kelog
*Facebook
HP
  
  6B. Sample of 5 US Universities
*Harvard
*Stanford
*UCSD
*UC Berkeley
UCLA
  
  6C. Sample of 5 Countries

*AMERICA!
*Canada
*Great Britain
*Australia
France
  
  6D. Sample of 5 Winners
*Malala
*Ernest Rutherford
*Obama
*Einstein
Kisinger
  
  7.
  
  7A. If an engineer wants to ensure the quality of their factory's production they can't possibly examine every single thing produced (census) due to time/money that would take, so they must take a sample. 
  
  7B. If a biologist wants to study how growing new plants next to other plants effects their growth they  would have to examine effectively every single pairing of two plants in the world unless those two were planted simultanously because their population of interest is plants with new plants near them, and there are probobly several billion cases, of that. They must thus take a sample. 
    
  7C. To get a census of an entire river you would need to test the entire river which is obviously impossible.
  
  7D. If a psycologist wants to know if "people" can memorie better while listening to music she would have to test all 7 billion of us to get a census. 
  
  8.  
    
  8A. The variables in this study are fish consumption and prostate cancer.  
    
  8B. Both variables seem to be treated mainly as categorical as we are dividing people into catagories, like no cancer/cancer or large consumption/never.  
    
  9.  
    
  9A. The variables in this study are Principal cause of Defect and Number of Defects.  
  
  9B. This is kind of trickey, number of defects for each principal cause is numeric, but the principal causes of defects is catagorical.  